### 2018-03-11 Sections/costs_and_attributes_in_quantum_networks.tex
Latin quotes done
Crypto, CV

\comment{Use term 'cost vector analysis' all over the place}
As with the classical case in Sec.~\ref{sec:costs}, there will be costs associated with the links and nodes in a network -- nothing is free! In the quantum case, all the usual classical costs are valid, but there are some very important additions of far greater relevance to most quantum applications. Classical digital data is discretised, resulting in data transmission highly robust against noise. In a quantum setting this is necessarily not the case, as the coefficients in quantum superpositions are continuous, meaning that errors accumulate during transmission and states will inevitably deteriorate, unlike digital states. This requires a rethinking of appropriate cost metrics.

\comment{Latin quote}\index{Latin}

@@

\comment{Two cost vectors: max and min loss of information, provides upper and lower bounds}

>>>>

As with the classical case in Sec.~\ref{sec:costs}, there will be costs associated with the links and nodes in a network -- nothing is free! In the quantum case, all the usual classical costs are valid, but there are some very important additions of far greater relevance to most quantum applications. Classical digital data is discretised, resulting in data transmission highly robust against noise. In a quantum setting this is necessarily not the case, as the coefficients in quantum superpositions are continuous, meaning that errors accumulate during transmission and states will inevitably deteriorate, unlike digital states. This requires a rethinking of appropriate cost metrics.

@@

### 2018-03-11 Sections/cryptowars.tex
Some restructuring and minor changes.
Crypto, CV

@@

\comment{How does AES work? Stream ciphers}

>>>>

%
% Computational vs Information-Theoretic Security
%

\subsection{Computational vs information-theoretic security}\index{Computational security}\index{Information-theoretic security}\label{sec:comp_vs_inf_th_sec}

Before describing any specific cryptographic protocols, let us define what is meant by `security' in a cryptographic context.

We differentiate between \textit{information theoretic security}\index{Information-theoretic security}, as opposed to \textit{computational security}\index{Computational security}.

In the former, the laws of quantum information bound the amount of information that can be extracted from a system, irrespective of measurement or computational operations. Thus, such security can be regarded as attack-independent.

In the latter, security is based on the assumption that an adversary's computational resources are insufficient to perform cryptanalysis or brute-force cracking. Clearly the former makes a far stronger statement about the security of a protocol than the latter.

Classical public- and private-key encryption protocols are typically based upon the assumption of computational security (e.g the computational complexity of performing integer factorisation in the case of RSA public-key encryption, or solving a complex satisfiability problem in the case of private-key encryption), whereas quantum encryption protocols are typically information theoretically secure (e.g the one-time-pad using QKD).

@@

### 2018-03-11 Sections/encrypted_cloud_quantum_computing.tex
Latin quote stubs
Crypto, CV

These encryption protocols induce a resource overhead in circuit size and number of qubits involved in the computation, with efficient scaling. They deliver (at least partially) information-theoretically secure\footnote{We differentiate between \textit{information theoretic security}\index{Information-theoretic security}, as opposed to \textit{computational security}\index{Computational security}. In the former, the laws of quantum information bound the amount of information that can be extracted from a system, irrespective of measurement or computational operations. Thus, such security can be regarded as attack-independent. In the latter, security is based on the assumption that an adversary's computational resources are insufficient to perform cryptanalysis or brute-force cracking. Clearly the former makes a far stronger statement about the security of a protocol than the latter. Classical public- and private-key encryption protocols are typically based upon the assumption of computational security (e.g the computational complexity of performing integer factorisation in the case of RSA public-key encryption, or solving a complex satisfiability problem in the case of private-key encryption), whereas quantum encryption protocols are typically information theoretically secure (e.g the one-time-pad using QKD).} data-hiding, enabling trustworthy outsourced processing of encrypted data, independent of the attack.

>>>>

These encryption protocols induce a resource overhead in circuit size and number of qubits involved in the computation, with efficient scaling. They deliver (at least partially) information-theoretically secure (Sec.~\ref{sec:comp_vs_inf_th_sec}) data-hiding, enabling trustworthy outsourced processing of encrypted data, independent of the attack.

### 2018-03-11 Sections/physical_architectures_for_quantum_computing.tex
Crypto, CV

A novel `double heralding'\index{Double heralding} technique, introduced in \cite{bib:BarrettKok05}, allows photon loss\index{Photon loss} to be overcome during which-path erasure \comment{Check this, is this what the double heralding does?}. Similarly, quantum states of light can be coupled to two-level quantum systems using Hamiltonians of the form shown in Eq.~(\ref{eq:two_level_hamil}). The preparation of long-distance entanglement between atomic systems has been demonstrated \cite{bib:Matsukevich05, bib:Matsukevich05b}

>>>>

A novel `double heralding'\index{Double heralding} technique, introduced in \cite{bib:BarrettKok05}, allows photon loss\index{Photon loss} to be overcome during which-path erasure. Similarly, quantum states of light can be coupled to two-level quantum systems using Hamiltonians of the form shown in Eq.~(\ref{eq:two_level_hamil}). The preparation of long-distance entanglement between atomic systems has been demonstrated \cite{bib:Matsukevich05, bib:Matsukevich05b}

### 2018-03-11 Sections/protocols_for_the_quantum_internet.tex
Latin quotes done
Crypto, CV

Each type of state being measured, in combination with the nature of the detection scheme, brings with it their own limitations. For example, number-resolved photo-detectors exhibit dead-time, are too slow to enable fast-feedforward, have spectral filtering characteristics, and mode-matching requirements. \comment{Is this right?}

>>>>

Each type of state being measured, in combination with the nature of the detection scheme, brings with it their own limitations. Specifications of interest include dead-time, speed (relevant when implementing feedforward), and spatio-spectral filtering characteristics.
